\section{Reduction based approach}

For simplicity let's focus on the function $OR_n \circ Parity_n$ and try to prove $\Omega(n)$ lower bound on width of $3$-round protocol. What we want is to do it in some kind of reduction-based style.

We think of player's inputs as vectors with $n$ coordinates each coordinate has value $\in \{0,1\}^n$. We want to try to implement the following strategy:

\begin{itemize}
    \item Suppose we have a $3$ round protocol for $OR_n \circ Parity_n$ of width $w$.
    
    \item The first message by Alice partitions the matrix $A \times B$ into $\leq 2^w$ rectangles. Pick $R = A_1 \times B$ - the best (probably just the largest) one of them.
    
    \item
    In $A_1$ an average coordinate has a high "diversity": 
    
    \[E_i[Pr_{x,y \in A_1}[x_i = x_j]] \approx 2^{-n + \frac{w}{n}}  \]
    
    \item
    We will fix few naughty coordinates of low density which hopefully will not decrease "diversity" of the rest of the coordinates by much.
    \item
    Now we want to say that the problem we end up with is hard.
\end{itemize}

To prove this we need to prove two lemmas. First tells us that after Alice's message we can pick a good subset of coordinates. This should be related to \cite{meir2017prediction}.

\begin{lemma}
    Suppose we have a set $S \subset A^k$, such that $|S| = \frac{|A|^k}{r}$. Then there is a subset of coordinates $I$ and values $a_i \in A$ for each $i \in I$, such that:
    
    \[ \forall j \not\in I:~  |\{r \in A| \exists x \in A:~  x_j = r, ~ \forall i \in I: ~ x_i = a_i\}| \gtrsim \frac{|A|}{r^{\frac{1}{k}}}  \]
    
\end{lemma}


The second lemma states that Parity is hard even if we have several instances to choose from:

\begin{lemma}
    For every set $S \subset Parity^{-1}(0)^k$, such that $\forall i \in [k]: |A_i| \geq \frac{2^{n-1}}{p}$ the following game is hard:
    
    \begin{itemize}
        \item Alice gets $a \in S$.
        
        \item Bob gets $b \in Parity^{-1}(1)^k$.
        
        \item Bob is allowed to send one message to Alice.
        
        \item Alice should output $i,j$ such that $a_{i,j} \neq b_{i,j}$
    \end{itemize}
    
    
\end{lemma}
